Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-25 src/tex/ms.tex
fix linebreak

\subsubsection{Simulated star and planet sample}
We generated two sets of synthetic exoplanet populations, one for FGK-type stars and one for M-type stars.
The stellar samples are drawn from the Gaia Catalogue of Nearby Stars~\citep{Smart2021} with a maximum Gaia magnitude of \var{M_G_max} and a maximum stellar mass of \var{M_st_max} \SI{}{\Msun}.
We included stars out to a maximum distance $d_{\max}$ that depends on the required planet sample size.
\revv{In our FGK sample, we find that K~dwarfs dominate with effective temperatures of $\var{median_T_eff_st_K_FGK}^{+\var{p84_T_eff_st_K_FGK}}_{-\var{p16_T_eff_st_K_FGK}}$~K and masses of $\var{median_M_st_K_FGK}^{+\var{p84_M_st_K_FGK}}_{-\var{p16_M_st_K_FGK}}$~$M_\odot$ (median and 16th/84th percentiles).
In the M~dwarf sample, the stars have effective temperatures of $\var{median_T_eff_st_M_M}^{+\var{p84_T_eff_st_M_M}}_{-\var{p16_T_eff_st_M_M}}$~K and masses of $\var{median_M_st_M_M}^{+\var{p84_M_st_M_M}}_{-\var{p16_M_st_M_M}}$~$M_\odot$.}

>>>>

\subsubsection{Simulated star and planet sample}
We generated two sets of synthetic exoplanet populations, one for FGK-type stars and one for M-type stars.
The stellar samples are drawn from the Gaia Catalogue of Nearby Stars~\citep{Smart2021} with a maximum Gaia magnitude of \var{M_G_max} and a maximum stellar mass of \var{M_st_max}~\SI{}{\Msun}.
We included stars out to a maximum distance $d_{\max}$ that depends on the required planet sample size.
\revv{In our FGK sample, we find that K~dwarfs dominate with effective temperatures of $\var{median_T_eff_st_K_FGK}^{+\var{p84_T_eff_st_K_FGK}}_{-\var{p16_T_eff_st_K_FGK}}$~K and masses of $\var{median_M_st_K_FGK}^{+\var{p84_M_st_K_FGK}}_{-\var{p16_M_st_K_FGK}}$~$M_\odot$ (median and 16th/84th percentiles).
In the M~dwarf sample, the stars have effective temperatures of $\var{median_T_eff_st_M_M}^{+\var{p84_T_eff_st_M_M}}_{-\var{p16_T_eff_st_M_M}}$~K and masses of $\var{median_M_st_M_M}^{+\var{p84_M_st_M_M}}_{-\var{p16_M_st_M_M}}$~$M_\odot$.}
